---
title: "BelkinElago data"
author: "Ashiqur"
date: "10/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## BelkinElago data exploratory analysis
Data set has been given by Danielle Sherman and the exploratory Analysis is given below :

#### load data set
```{r BelkinElago}
Belkin<-read.csv2("BelkinElagoComplete.csv")
```


#### Summary Function
summary function gives us the min, max, mean, median, and quartiles of each attribute

```{r}
summary(Belkin)
#hist(Belkin$age)
#plot(Belkin$age,Belkin$elevel)#
#cor(Belkin$age,Belkin$car)
```
#### Head of the data set
```{r}
head(Belkin)

```
####df_status()
gives information on the structure of the dataframe and the data it contains, such as variable names and data types
```{r  echo=TRUE}
#library(DataExplorer)
library(funModeling)
#plot_str(Belkin)//// Output doesn't show in the html file
df_status(Belkin)
```


#### Histogram of salary,age,credit(used for one continuous)
salary,age data is not normaly distributed but credit data is normaly distributed 
```{r pressure, echo=TRUE}

#salary
library(ggplot2)
salary_his <- ggplot(Belkin,aes(x=salary))
salary_his + geom_histogram(binwidth=1000,color='red',fill='pink')

#age
library(ggplot2)
age_his <- ggplot(Belkin,aes(x=age))
age_his + geom_histogram(binwidth=1,color='red',fill='pink')

#credit
library(ggplot2)
credit_his <- ggplot(Belkin,aes(x=credit))
credit_his + geom_histogram(binwidth=1,color='red',fill='pink')

```
#### Barplots(used for one continuous)

```{r  echo=TRUE}
library(ggplot2)
#-------------------------------------elevel bar plot---------#
## counts (or sums of weights)
belkin_bar<- ggplot(Belkin, aes(elevel))
# Number of people in each education level:
#belkin_bar + geom_bar(color="red",fill="black")
Belkin$elevel<-as.factor(Belkin$elevel)
belkin_bar + geom_bar(color="red",fill="black")
belkin_bar + geom_bar(aes(fill = elevel))#color seperated by elevel
belkin_bar + geom_bar(aes(fill = brand),position = "fill")#color seperated by brand
belkin_bar + geom_bar(aes(fill = brand),position = "dodge")#color seperated by brand in two bar

#-------------------------------------car bar plot--------------------#
belkin_bar<- ggplot(Belkin, aes(car))
belkin_bar + geom_bar(aes(fill = brand))#color seperated by brand
belkin_bar + geom_bar(aes(fill = elevel))#color seperated by elevel

#-------------------------------------Zipcode bar plot--------------------#
belkin_bar<- ggplot(Belkin, aes(zipcode))

belkin_bar + geom_bar(aes(fill = brand))#color seperated by brand
belkin_bar + geom_bar(aes(fill = elevel))#color seperated by elevel

belkin_bar + geom_bar(aes(fill = brand),position = "dodge")#color seperated by brand in two bar


```
###Scatterplots(used for two continuous)

```{r  echo=TRUE}
library(ggplot2)
belkin_scatt <- ggplot(data=Belkin,aes(x = age,y=salary)) 
belkin_scatt  + geom_point(aes(color=factor(brand)))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
